### 2021-12-16 documentos/generators.tex
A medias con el párrafo sobre simetrías PCEGs

In this section we will discuss the existence of a generator set for all PCE
quantum channels, how to label each of them uniquely according to its local-action 
on every qubit in the system, and, finally, we  	will discuss a symmetry of
both PCE quantum channel generators and $A$, the matrix that diagonalizes
the Choi matrix $\mcD_N$ of a PCE map.

@@

%\cpnote{Arreglar}
PCE generators may be characterized by its local-action on every qubit 
in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
with $\vec\alpha$ each of the $4^{n}$ different vector indices. For 1-qubit
the PCE generators are the identity map plus the channels that map the Bloch 
sphere to each Cartesian axis, as their associated vector subspaces are trivial
to prove and their dimension 1 is met. 
\janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
\pce{} generators}
Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ with the local-action
of the PCE generator on the $k$-th qubit. In consequence, we will denote 
PCE generators as $\mcG_{\vec\alpha}$. 
See, for example, that the 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

%\cpnote{Mucha lora y no se prueba nada}
A symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ the diagonalizes a PCE map's Choi matrix $\mcD_N$.
%PCE generators $\pceg$ obey a symmetry
%that defines uniquely every PCE generator. 
For a PCE generator the symmetry is encoded in the parameters $\{\taus\}$, and 
for $A$ in its rows and columns.
The $N$-dimensional Cartesian grid associated with $\{\tau_{\vec\alpha}\}$
is either symmetric or anti-symmetric with respect to
the $N$ hyperplanes of dimension $N-1$ that divide the grid in half.
For instance, see that the diagrams representing the generators 
$\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$ in subfigures 
(c), (d) and (e) of \Fref{fig:two:qubit:examples}, respectively,
are either symmetric or anti-symmetric with respect to the lines that divide vertically 
and horizontally the diagrams in half. In fact, this symmetry may be used to
construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$
and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
anti-symmetric to the previous subset. For example, let us illustrate the 
procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
eight.

>>>>

In this section we will discuss the existence of a generator set for all PCE
quantum channels, how to label each of them uniquely according to its local action 
on every qubit in the system, and, finally, we  	will discuss a symmetry of
both PCE quantum channel generators and $A$, the matrix that diagonalizes
the Choi matrix $\mcD_N$ of a PCE map.

@@

%\cpnote{Arreglar}
PCE generators may be characterized by its local action on every qubit 
in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
with $\vec\alpha$ each of the $4^{n}$ different vector indices. For 1-qubit
the PCE generators are the identity map plus the channels that map the Bloch 
sphere to each Cartesian axis, as their associated vector subspaces are trivial
to prove and their dimension 1 is met. 
\janote{Here goes the bla bla for the discussion of the proof for the $N$-qubit
\pce{} generators}
Therefore, we can identify the index $\alpha_k$ in $\vec\alpha$ by the local action
of the PCE generator on the $k$-th qubit. 
See, for example, that the 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

%\cpnote{Mucha lora y no se prueba nada}
A reflection symmetry is identified for both PCE generators $\pceg$ and
the matrix $A$ that diagonalizes the Choi matrix $\mcD_N$ of a PCE map.
%PCE generators $\pceg$ obey a symmetry
%that defines uniquely every PCE generator. 
The symmetry for a PCE generator $\pceg$ is encoded in the 
parameters $\{\taus\}$, the $N$-dimensional Cartesian grid associated with it 
(the set) is either symmetric or anti-symmetric under reflection of the 
indices in the $k$-th position in $\vec\alpha$ as
\begin{align}
\alpha_{0}\mapsto\alpha_3,\quad\alpha_{3}\mapsto\alpha_0,
\quad\alpha_1\mapsto\alpha_2, \quad\alpha_2\mapsto\alpha_1.
\end{align}
the $N$ hyperplanes of dimension $N-1$ that divide the grid in half.
For instance, see that the diagrams representing the generators 
$\mcG_{(1,3)}$, $\mcG_{(3,2)}$ and $\mcG_{(2,2)}$ in subfigures 
(c), (d) and (e) of \Fref{fig:two:qubit:examples}, respectively,
are either symmetric or anti-symmetric with respect to the lines that divide vertically 
and horizontally the diagrams in half. In fact, this symmetry may be used to
construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$
and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
anti-symmetric to the previous subset. For example, let us illustrate the 
procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
eight.
